---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# schelp

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/schelp)](https://CRAN.R-project.org/package=schelp)
<!-- badges: end -->

The goal of schelp is to ...

## Installation

You can install the development version of schelp from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("wvictor14/schelp")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example, eval = FALSE}
library(schelp)
## basic example code
```

## development: subset data

A small subset ~1% of Smillie2019 gut scRNAseq data has been added for testing
and development. It is accessible as `counts` and `metadata`.

## development: full data

